\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-05 R/clean_spectral_data.Rmd
results OA table and spectra figure

```{r, eval = FALSE, include = "FALSE", warning=FALSE, fig.height=12, fig.width=16}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID)) +
  geom_path(alpha = .2, color = "#1c9099") +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n') + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=5) +
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14))

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 9)
```

>>>>

```{r, eval = FALSE, include = "FALSE", warning=FALSE, fig.height=8, fig.width=10}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID)) +
  geom_path(alpha = .2, color = "#1c9099") +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n') + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=5) +
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14))

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 8)
```

### 2020-11-05 analysis/paper/paper.Rmd
results OA table and spectra figure

knitr::kable(x = df, 
             # set column names
             col.names = c("Overall Accuracy (%):",
                           "Species Classification",
                           "Genus Classification"),
             # center align text in the columns
             align = c("c", "c", "c"),
             format = "simple")
```

>>>>

knitr::kable(x = df, 
             # set column names
             col.names = c("Overall Accuracy [%]",
                           "Species Classification",
                           "Genus Classification"),
             # center align text in the columns
             align = c("c", "c", "c"),
             format = "simple")
```
